---
title: "August_9th"
author: "Zhihao Chen"
date: "2023-08-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## August_9th

### Logarithmic 
#### Softmax function

```{r}
y <- 1:3
numer <- exp(y)
denom <- sum(exp(y))
softmax <- numer / denom # proportion/weights

y <- c(1e3, 1e3+1, 1e3+2)
exp(y) 


```

This produces overflow - numbers are too big for the computer

```{r}
# log softmax
LSE <- function(x) {
  c <- max(x)
  y <- c + log(sum(exp(x - c)))
  return(y)
}

log_softmax <- function(x) {
  x - LSE(x)
}

softmax_unsafe <- function(x) exp(x)/sum(exp(x))

softmax_unsafe(1:3)
exp(log_softmax(1:3)) # bring back the actual softmax

softmax_unsafe(y) # large numbers won't work
exp(log_softmax(y)) # work
```

### Limits
Position as a function of time t

You guess that the function is a quadratic in t. If x is measured in meters, and t is in seconds, then a must have units of m and b must have units m/s^2. 

$$
x(t) = a + bt^2
$$
This is a linear function, as parameters a and b are linear, the predictor t^2 does not has to be linear. 

$$
a(t) = \frac{dv}{dt} = \frac{d}{dt}\frac{dx}{dt} = \frac{d^2x}{dt^2}
$$

Approximating Derivatives

```{r}
library(ggplot2)
library(dplyr)

n <- 100
t <- seq(0, pi, length = n)
x <- sin(t) * cos(t)
dxdt <- cos(t)^2 - sin(t)^2

d <- tibble(t, x, dxdt)

ggplot(d, aes(t, x)) + geom_line(aes(y = dxdt), color = "red")
```

### Map Funtion
Better substitution for loop in R

```{r}
# create 
x <- 1:10
y <- x %>% 
  map(\(x) runif(n=100, min=x, max=15)) 
# \(x) is an def of function, the back slash is a syntax expression, just a shorthand of initiating a function
# look for the Advanced R for more 

y
```

### Data Transformation, Pivot Functions

```{r}
rates <- seq(0.05, 0.2, length = 10) # rate for comparison, 5% to 20%
P <- 100
time <- seq(1, 50, length = 50)

Pe <- function(A, r, t) A*exp(r*t) # get Pe curve at every time t
d <- time %>% map(\(x) Pe(A = P, r = rates, t = x))

names(d) <- as.character(time)
d <- as_tibble(d)

#....
```


### Integration

```{r}

```























