---
author: "Zhihao Chen"
date: "2023-08-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(MASS)
```


## HW5 Questions

Suppose a deck of cards contains 4 red cards and 6 blue cards. Two cards are drawn sequentially without replacement. Calculate the probability that the second card drawn is red, given that the first card drawn was blue.

```{r}
sample <- c(rep("R", 4), rep("B", 6)) 
func <- function(x) {sample(x, 2, replace = F)}
x <- replicate(1e5, func(sample))

B_idx <- which(x[1, ] == "B")
B_sample_space <- x[, B_idx]
R_idx <- which(B_sample_space[2, ] == "R")
length(R_idx) / length(B_idx)
```


A certain disease affects 2% of the population. A diagnostic test for the disease is known to produce a false positive result 5% of the time and a false negative result 3% of the time. If a randomly selected person tests positive for the disease, what is the probability that they actually have the disease?

Follow this with the covid case example from slides. 

```{r}

```


Consider two fair six-sided dice, one red and one green. The red die has the numbers 1 through 6, and the green die has the numbers 2 through 7. What is the probability that the sum of the two dice is 8, given that the red die shows an even number?

```{r}
R<- 1:6
G <- 2:7
sums <- outer(R, G, FUN = "+")
colnames(sums) <- str_c(R, "R")
rownames(sums) <- str_c(G, "G")

sums

# P(S = 8 | Red = even)
# P(S = 8 | Red = even) = P(S = 8 AND Red = even) / P(Red = even)
# P(S = 8 AND Red = even) = 3/36 = 1/12
# P(Red = even) = 1/2 
# P(S = 8 | Red = even) = (1/12) / (1/2) = 1/6 

# P(S = 8) id P(Red = even)
# If independent, P(A|B) = P(A)P(B)
# P(S = 8) = 8/36 = 2/9
# P(Red = even) = 1/2
```


## Session 5

The Monty Hall Problem

If not open any door, its always 1/3
If open one door that is not a car, its 2/3

Done with simulation

```{r}

```



## Random Variables

Random variable X for the number of Heads in two flips.

- Discrete RV ==> CDF (Cumulative Distribution Function) & PMF (Probability Mass Function)
- Continuous RV ==> PDF (Probability Density Function)

CDF $F_X(x)$ is a function of x and is bounded between 0 and 1:

$$
F_X(x) = P(X \le x)
$$

PMF (for discrete RVs only) $f_X(x)$ is a function of x:

$$
f_X(x) = P(X = x)
$$

You can get from $f_X$ to $F_X$ by summing. Let's say x = 4. In that case:

$$
missing
$$

#### Some R RV Conventions

- In R, PMFs and PDFs start with the letter d. For example dbinom() and dnormal() refer to binomial PMF and normal PDF. 
- CDFs start with p, so pbinom() and pnorm(). 
- Random number generators start with r, so rbinom(). 
- Look for dbinom(x, size, prob, log, replace = FALSE)


## Binomial RV

Binomial PMF
- Bernoulli RV is one coin flip with a set probability of success (say Heads)
- if $X \sim Bernoulli(\theta)$, the PMF can be written directly as

$$
P(X = x) = \theta^x(1-\theta)^{1-x}, x\in\{0, 1\}
$$
- Binomial can be thought of as the sum of N independent Bernoulli trials. We can also write:

$$
Bernoulli(x|\theta) = \begin{cases}
  \theta  &  \text{if x = 1 and } \\
  1- \theta &  \text{if x = 0}
\end{cases}
$$

- We can write the Binomial PMF, $X \sim Bernoulli(N,\theta)$ this way:

$$
Binomial(x | N, \theta) = {N \choose x} \theta^x(1-\theta)^{N-x}
$$

C(n,r) = n! / r! (n – r)! = 4! / 2!


## PMF and CDF Plots

$Binomial(x | N = 4, \theta = 1/2)$


## Binomial in R

```{r}
# What is the p of getting 2 heads out of 5 fair trails?
N <- 5; x <- 2
dbinom(x = x, size = N, prob = .5) %>% fractions()

# What is the binomial PMF: P(X = x), for N = 5, p = 0.5?
N <- 5; x <- -2:7
dbinom(x, N, prob = 0.5) %>% fractions()

# Verify that the PMF sums to 1
sum(dbinom(x, N, 0.5))

# What is the p of 3 heads or fewer
pbinom(3, N, 0.5) %>% fractions() # this is a PMF, where x = 3

# compute the CDF: P(X <= x), for N = 5, p = 0.5
pbinom(x, N, 0.5) %>% fractions() # this is all, cumulative

# get the PMF to CDF with cumsum()
dbinom(x, N, 0.5) %>% cumsum() %>% fractions()

# Practice: p = 1/3, N = 10, p of getting 6 or more success? Compute with PDF, verify with CDF
dbinom(6:10, size = 10, prob = 1/3) %>% sum() # compute with PDF
1- pbinom(5, 10, 1/3) # verify with CDF
# (10 choose 6) * (1/3)^6 * (1-1/3)^(10-6)
```


## Geometirc RV

- Geometric is a discrete waiting time distribution, and Exponential is its continuous analog
- If X is the number of failures before first success $X \sim Geometric(\theta)$, where $\theta$ is probability of success. 
- Example would be keep flipping coin until we get success, say Heads
- If x is the number of failures, the PMF is $P(X = x)=(1-\theta)^x\theta$

- To check if this is a valid PMF we need to sum over all x:

$$
\sum^\infty_{x=0}\theta(1-\theta)^x = \theta\sum^\infty_{x=0}(1-\theta)^x \\
let\ u = 1- \theta

$$
























